### 2023-09-07 Paper/main.tex
Add bibliography at bottom
Adapt filesize comparison plot size
Add SSIM metric (#70)

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\bibliography{shortbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Set this to true to remove the border
    linkcolor=black, % Color for internal links
    citecolor=black, % Color for citations
    }
\usepackage{listings}
\usepackage{blindtext}
\usepackage{geometry}
\geometry{margin=25mm}
\begin{document}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{filesize_comparison.png}
	\caption{Archived filesizes for used encoder}
	\label{fig: fsize_comparison}
\end{figure}

\noindent
To ensure the proper functioning of the employed encoder, we conducted calculations of Peak Signal to Noise Ratio (PSNR) and generated plots depicting its relationship with the achieved compression rates. To maintain clarity in the plots, we utilized JPEGXR with its default overlapping parameter (1).

\begin{figure}[h!]
	\centering
	\includegraphics[width=8cm]{psnr.png}
	\caption{PSNR comparison of the used codecs}
	\label{fig: psnr_comparison}
\end{figure}

\noindent
As anticipated, the results presented in plot \ref{fig: psnr_comparison} affirm that the plain JPEG encoder consistently yields in reduced-quality images when operating at lower compression rates.
The driving motivation behind this attempt was to intentionally introduce diverse encoding artifacts into the compressed images for later train a model and classify the used image encoder.
\newpage

@@

\end{document}

>>>>

\documentclass{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{graphicx} % Required for inserting images
\usepackage{biblatex}
\bibliography{shortbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Set this to true to remove the border
    linkcolor=black, % Color for internal links
    citecolor=black, % Color for citations
    }
\usepackage{listings}
\usepackage{blindtext}
\usepackage{cleveref}
\usepackage{subcaption}
\geometry{margin=25mm}
\begin{document}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=12cm]{filesize_comparison.png}
	\caption{Archived filesizes for used encoder}
	\label{fig: fsize_comparison}
\end{figure}

\noindent
To validate the performance of the utilized encoder, we carried out assessments involving two key metrics: Peak Signal to Noise Ratio (PSNR) and Structural Similarity Index (SSIM). Both metrics got calculated as mean values over 5 images. These evaluations were displayed in plot \ref{fig: comparison} to generate graphical representations illustrating the correlation between these metrics and the resultant compression rates. To ensure visual clarity within the plots, we employed the JPEGXR compression algorithm with its default overlapping parameter set to 1.

\begin{figure}[h!]
    \centering
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{psnr.png}
          \caption{PSNR comparison of the used codecs}
          \label{fig: psnr_comparison}
      \end{subfigure}
      \hfill
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{ssim.png}
          \caption{SSIM comparison of the used codecs}
          \label{fig:CI}
      \end{subfigure}
\caption{
\label{fig: comparison}%
Comparison of PSNR and SSIM}
\end{figure}

\noindent
As anticipated, the results presented in plot \ref{fig: comparison} affirm that the plain JPEG encoder consistently yields in reduced-quality images when operating at lower compression rates.
The driving motivation behind this attempt was to intentionally introduce diverse encoding artifacts into the compressed images for later train a model and classify the used image encoder.
\newpage

@@

\printbibliography
\end{document}
